Model2

### 2020-11-16 Model_2.rmd
model 2 update, Please enter the commit message for your changes. Lines starting

---
title: "Untitled"
output: pdf_document
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(lmtest)
library(sandwich)
library(stargazer)
library(magrittr)
library(ggplot2)
library(patchwork)

knitr::opts_chunk$set(echo = TRUE)
```

```{r}
D = read.csv("covid-19.csv")
```
## List of Demographic Variables  
COVID-19 Cases by Race/Ethnicity:
 - white % of Total Population,
 - Black % of Total Population, 
 - Hispanic % of Total Population, 
 - Other % of Total Population

@@

Demographics:
	➤Children 0-18, ➤Adults 19-25, ➤Adults 26-34,  ➤Adults 35-54, ➤Adults 55-64, ➤65+

## Data Explorary

a) Varialbe of Case Rate per 100000 is of nearly normal distribution.

```{r}
summary(D$Case.Rate.per.100000)

@@

```{r}
ggplot(data = D,
  mapping = aes(x= Case.Rate.per.100000))+
  geom_histogram(fill = 'skyblue', color = 'grey30', breaks = seq(0,6000,600)) +
  labs(title =  "Histogram of Case rate per 100000", x = "Case per 100000", y = 'Count')+
  scale_x_continuous(breaks=seq(0, 6000, 600))
```

b) Varialbe of Population density per squres 
The distribution of the Population density per squres clusters at the two ends, which is caused by the extremely high population density of District of Columbia (11496.81) compared to the 50 states.
While, the logrithm of population density is close to a normal distribution. In addtion, an analysis excluding the District of Columbia is another option. 
```{r}
summary(D$Population.density.per.square.miles)
```
District of Columbia is extremely high population density than all 50 states
```{r}
hist_population_dens <- ggplot(data = D,
  mapping = aes(x= Population.density.per.square.miles))+
  geom_histogram(fill = 'skyblue', color = 'grey30', breaks = seq(0,12000,500)) +
  labs(title =  "Histogram of Population density", x = "Population density per square miles", y = 'Count')+
  scale_x_continuous(breaks=seq(0, 12000, 1200))

hist_log_population_dens <- ggplot(data = D, aes(x = log(Population.density.per.square.miles))) + 
  geom_histogram(fill = 'skyblue', color = 'grey30', breaks = seq(0,10,1)) + 
  labs(title = 'Histogram of Population density', x = 'Log Population density per square miles', y = 'Count')

@@

```
c) White % of Total Population/ Black % of Total Population

Three entries of Black % of total population is "<0.01", which is to be dropped or replaced by values determined by extra resources for further analysis.

In addition, white % of total population and black % of total population could be highly related. (Correlation of these two vairalbes need to be investigated after cleaning the black % variables)

The distribution of the white % is skewed, not a ideal normal distribution. While the distribution of the square of white % is more close to a normal distribution. 
```{r}
D$Black...of.Total.Population
#cor(D$White...of.Total.Population, D$Black...of.Total.Population)
```

```{r}
summary(D$White...of.Total.Population)
```

```{r}
ggplot(data = D,
  mapping = aes(x= White...of.Total.Population))+
  geom_histogram(fill = 'skyblue', color = 'grey30', breaks = seq(0,1,0.05)) +
  labs(title =  "Histogram of White Percentage", x = "White % of Total Population", y = 'Count')+
  scale_x_continuous(breaks=seq(0, 1, 0.1))
```
```{r}
ggplot(data = D,
  mapping = aes(x= (White...of.Total.Population)^2))+
  geom_histogram(fill = 'skyblue', color = 'grey30', breaks = seq(0,1,0.05)) +
  labs(title =  "Histogram of White Percentage", x = "White % of Total Population", y = 'Count')+
  scale_x_continuous(breaks=seq(0, 1, 0.1))
```

d) Percent living under the federal poverty line 2018

Correlation of pecent living under poverty line and white percentage of total population shows that they are related.

The distribution is not heavily skewed.

```{r}
summary(D$Percent.living.under.the.federal.poverty.line..2018.)
cor(D$Percent.living.under.the.federal.poverty.line..2018., D$White...of.Total.Population)
```

```{r}
ggplot(data = D,
  mapping = aes(x= Percent.living.under.the.federal.poverty.line..2018.))+
  geom_histogram(fill = 'skyblue', color = 'grey30', breaks = seq(6,21,1)) +
  labs(title =  "Histogram of Percent of poverty 2018", x = "Percent.living.under.the.federal.poverty.line", y = 'Count')+
  scale_x_continuous(breaks=seq(6, 21, 1))
```

e)
```

@@

## Model 2

No obvious trend could be observed or concluded from the plots.

```{r}
D %>% 
  ggplot(aes(log(Population.density.per.square.miles), Case.Rate.per.100000, color = White...of.Total.Population)) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to Population Density', 
    x = 'Log Population Density', 
    y = 'Case.Rate.per.100000',
    color = 'White %'
  )
```
```{r}
D %>% 
  ggplot(aes(x = log(Population.density.per.square.miles), y = Case.Rate.per.100000, color = Percent.living.under.the.federal.poverty.line..2018.)) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to Population Density', 
    x = 'log Population Density', 
    y = 'Case.Rate.per.100000',
    color = 'Poverty Percentage'
  )
```

```{r}
D %>% 
  ggplot(aes(x = White...of.Total.Population, y = Case.Rate.per.100000, color = Percent.living.under.the.federal.poverty.line..2018.)) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to White %', 
    x = 'White % of Total Population', 
    y = 'Case.Rate.per.100000',
    color = 'Poverty Percentage'
  )
```

```{r}
D %>% 
  ggplot(aes(x = Percent.living.under.the.federal.poverty.line..2018., y = Case.Rate.per.100000, color = log(Population.density.per.square.miles))) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to Poverty %', 
    x = 'Percent.living.under.the.federal.poverty.line..2018.', 
    y = 'Case.Rate.per.100000',
    color = 'log(Population Density)'
  )
```

## Model 1-a
$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 Population.Density.Per.Square.Miles
\end{aligned}
$$

```{r}
model1a <- lm(Case.Rate.per.100000 ~ Population.density.per.square.miles, data = D)
coeftest(model1a, vcov = vcovHC)
```
## Model 1-b
$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 log(Population.Density.Per.Square.Miles)
\end{aligned}
$$
```{r}
model1b <- lm(Case.Rate.per.100000 ~ log(Population.density.per.square.miles) , data = D)
coeftest(model1b, vcov = vcovHC)

```
## Model 2-a
$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 log(Population.Density.Per.Square.Miles)\\ &+ \beta_2(White.Percentage.of.total. population)
\end{aligned}
$$

```{r}
model2a <- lm(Case.Rate.per.100000 ~ log(Population.density.per.square.miles)+ White...of.Total.Population, data = D)
coeftest(model2a, vcov = vcovHC)

#model2a <- lm(Case.Rate.per.100000 ~  White...of.Total.Population, data = D)
#coeftest(model2a, vcov = vcovHC)
```
$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 log(Population.Density.Per.Square.Miles)\\ &+ \beta_2(White.Percentage.of.total. population)^2
\end{aligned}
$$
```{r}
model2a <- lm(Case.Rate.per.100000 ~ log(Population.density.per.square.miles)+ I((White...of.Total.Population)^2), data = D)
coeftest(model2a, vcov = vcovHC)

@@

## Model 2-b
$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 log(Population.Density.Per.Square.Miles)\\ &+ \beta_2(White.Percentage.of.total. population)\\ &+\beta_3(Percen.living.under.the.federal.poverty.line.2018)
\end{aligned}
$$

```{r}
model2b <- lm(Case.Rate.per.100000 ~log(Population.density.per.square.miles)+ White...of.Total.Population+Percent.living.under.the.federal.poverty.line..2018., data = D)
coeftest(model2b, vcov = vcovHC)

@@

$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 log(Population.Density.Per.Square.Miles)\\ &+ \beta_2(White.Percentage.of.total. population)^2\\ &+\beta_3(Percen.living.under.the.federal.poverty.line.2018)
\end{aligned}
$$
```{r}
model2b <- lm(Case.Rate.per.100000 ~log(Population.density.per.square.miles)+ I((White...of.Total.Population)^2) + Percent.living.under.the.federal.poverty.line..2018., data = D)
coeftest(model2b, vcov = vcovHC)

## Limitations

I.I.D assumption for CLM is not satisfied perfectly for all the models discussed above, since the states are not isolated from each other. It is impossible states suffered from pandmice at randomly different levels. Actually, the pandemic status across states may be highly related to each other.

In addition, all states are involved in the same market economy system even though there are econoy perfermance divisions across the states. Moreover, in most states white race is still dominant in the population. Many states share similar racial composition.

>>>>

---
title: "Model2"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tinytex)
library(tidyverse)
library(lmtest)
library(sandwich)
library(stargazer)
library(magrittr)
library(ggplot2)
library(patchwork)
```

```{r}
df = read.csv("covid-19.csv")
```

## Model 2 Building Process
Part of the model aims to investigate the relationship between the covid-19 pandemic status and the state demographic information. The list of demographic variables included in the current dataset is as below.

COVID-19 Cases by Race/Ethnicity:
 - white % of Total Population,
 - Black % of Total Population, 
 - Hispanic % of Total Population, 
 - Other % of Total Population

@@

Demographics:
 -Children 0-18
 - Adults 19-25
 - Adults 26-34
 - Adults 35-54
 - Adults 55-64
 - 65+

Currently, Case Rate per 100000 is chosen as a dependent variable to represent the pandemic status in each state. Variables as Population density per square miles, Percent Unemployed (2018)/Percent living under the federal poverty line (2018), White % of of Total Population/Black % of Total Population, Percentage of 65+ are chosen as candidate covariates to explore potential connection between pandemic status demographic characteristics, economy status, racial composition.

Through data explorary, most data investigated is clean as numberica type except the black percentage of total population. This information of some states is reported vaguely as less than 0.01, which is replaced as 0 for further work. This could be updated with more precise data with the help of external resources.

Several transformations have been made for variables a Population density per square miles and White % of Total Population.

### Data Explorary
Through data explorary, most data investigated is clean as numberica type except the black percentage of total population. This information of some states is reported vaguely as less than 0.01, which is replaced as 0 for further work. This could be updated with more precise data with the help of external resources.

Several transformations have been made for variables a Population density per square miles and White % of Total Population. Population density is extremely skewed due to the high population density of the District of Columbia.  A logarithm transformation of this variable is of more uniform distribution. In addition, the square of the white percentage of the total population is of a distribution closer to the normal distribution. It also represents the chance that the interaction happens between two white people in practice.

In addition, correlation values of White% and Black %, Percent Unemployed and Percent living under the federal poverty line shows these two groups of variables are correlated respectively. 
#### 1-a) Varialbe of Case Rate per 100000 is of nearly normal distribution.

```{r}
summary(df$Case.Rate.per.100000)

@@

```{r}
ggplot(data = df,
  mapping = aes(x= Case.Rate.per.100000))+
  geom_histogram(fill = 'skyblue', color = 'grey30', breaks = seq(0,6000,600)) +
  labs(title =  "Histogram of Case rate per 100000", x = "Case per 100000", y = 'Count')+
  scale_x_continuous(breaks=seq(0, 6000, 600))
```

#### 1-a) Varialbe of Population density per squres 
The distribution of the Population density per squares clusters at the two ends, which is caused by the extremely high population density of District of Columbia (11496.81) compared to the 50 states.
While, the logarithm of population density is close to a normal distribution. In addition, an analysis excluding the District of Columbia is another option.

```{r}
summary(df$Population.density.per.square.miles)
```
District of Columbia is extremely high population density than all 50 states
```{r}
hist_population_dens <- ggplot(data = df,
  mapping = aes(x= Population.density.per.square.miles))+
  geom_histogram(fill = 'skyblue', color = 'grey30', breaks = seq(0,12000,500)) +
  labs(title =  "Histogram of Population density", x = "Population density per square miles", y = 'Count')+
  scale_x_continuous(breaks=seq(0, 12000, 1200))

hist_log_population_dens <- ggplot(data = df, aes(x = log(Population.density.per.square.miles))) + 
  geom_histogram(fill = 'skyblue', color = 'grey30', breaks = seq(0,10,1)) + 
  labs(title = 'Histogram of Population density', x = 'Log Population density per square miles', y = 'Count')

@@

```
#### 2-a) White % of Total Population/ Black % of Total Population

Variable of Black % is stored as string variables. Moreover, three entries of Black % of total population is "<0.01", which is to be dropped or replaced by values determined by extra resources for further analysis.

Here, the value of Black % is replaced by 0 when it is "<0.01". Afterwards, the correlation of white % and black % is -0.42, which shows these two variables are correlated. Considering that the value of other race groups is much smaller, it is proper to only include White% in the regression model to explore the relation of care rate and racial composition.

The distribution of the white % is skewed, not an ideal normal distribution. While the distribution of the square of white % is more close to a normal distribution. In practice, this square could reflect the chance that the interaction happens between two white people.

```{r}
black_num <- as.numeric(df$Black...of.Total.Population)
black_num[is.na(black_num)]<- 0
cor(df$White...of.Total.Population, black_num)

@@

```{r}
summary(df$White...of.Total.Population)
```

```{r}
ggplot(data = df,
  mapping = aes(x= White...of.Total.Population))+
  geom_histogram(fill = 'skyblue', color = 'grey30', breaks = seq(0,1,0.05)) +
  labs(title =  "Histogram of White Percentage", x = "White % of Total Population", y = 'Count')+
  scale_x_continuous(breaks=seq(0, 1, 0.1))
```
```{r}
ggplot(data = df,
  mapping = aes(x= (White...of.Total.Population)^2))+
  geom_histogram(fill = 'skyblue', color = 'grey30', breaks = seq(0,1,0.05)) +
  labs(title =  "Histogram of White Percentage", x = "White % of Total Population^2", y = 'Count')+
  scale_x_continuous(breaks=seq(0, 1, 0.1))
```

#### 2-b) Percent living under the federal poverty line 2018

Correlation of pecent living under poverty line and white percentage of total population shows that they are related. The distribution is not heavily skewed.

```{r}
summary(df$Percent.living.under.the.federal.poverty.line..2018.)
cor(df$Percent.living.under.the.federal.poverty.line..2018., df$White...of.Total.Population)
```

```{r}
ggplot(data = df,
  mapping = aes(x= Percent.living.under.the.federal.poverty.line..2018.))+
  geom_histogram(fill = 'skyblue', color = 'grey30', breaks = seq(6,21,1)) +
  labs(title =  "Histogram of Percent of poverty 2018", x = "Percent.living.under.the.federal.poverty.line", y = 'Count')+
  scale_x_continuous(breaks=seq(6, 21, 1))
```
#### 2-c) Percent Unemployed 2018
Although, the distribution is of high peak in the middle of the range. Overall, it is not highly skewed or heavily tailed. In addition, the unemployed rate is correlated to the variable to the poverty rate, which is in an agreement with intuitive expectation.

```{r}
summary(df$Percent.Unemployed..2018.)
cor(df$Percent.Unemployed..2018., df$Percent.living.under.the.federal.poverty.line..2018.)
```
```{r}
ggplot(data = df,
  mapping = aes(x= Percent.Unemployed..2018.))+
  geom_histogram(fill = 'skyblue', color = 'grey30', breaks = seq(0,10,1)) +
  labs(title =  "Histogram of Unemployed percentage", x = "Percent.Unemployed..2018.", y = 'Count')+
  scale_x_continuous(breaks=seq(0, 10, 1))
```

#### 2-d) Age 65+ Percentage
The 65+ percentage is of a nearly normal distribution.

```{r}
summary(df$X65.)
```
```{r}
ggplot(data = df,
  mapping = aes(x= X65.))+
  geom_histogram(fill = 'skyblue', color = 'grey30', breaks = seq(0.10,0.22,0.01)) +
  labs(title =  "Histogram of Percent of 65+", x = "65+ Percentage", y = 'Count')+
  scale_x_continuous(breaks=seq(0.1, 0.25, 0.05))
```

### Plot 
No obvious trend could be easily observed or concluded from the plots regarding the dependent variables and candidate covariates.

```{r}
df %>% 
  ggplot(aes(log(Population.density.per.square.miles), Case.Rate.per.100000, color = White...of.Total.Population)) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to Population Density', 
    x = 'Log Population Density', 
    y = 'Case.Rate.per.100000',
    color = 'White %'
  )
```
```{r}
df %>% 
  ggplot(aes(x = log(Population.density.per.square.miles), y = Case.Rate.per.100000, color = Percent.living.under.the.federal.poverty.line..2018.)) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to Population Density', 
    x = 'log Population Density', 
    y = 'Case.Rate.per.100000',
    color = 'Poverty Percentage'
  )
```

```{r}
df %>% 
  ggplot(aes(x = White...of.Total.Population, y = Case.Rate.per.100000, color = Percent.living.under.the.federal.poverty.line..2018.)) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to White %', 
    x = 'White % of Total Population', 
    y = 'Case.Rate.per.100000',
    color = 'Poverty Percentage'
  )
```

```{r}
df %>% 
  ggplot(aes(x = Percent.living.under.the.federal.poverty.line..2018., y = Case.Rate.per.100000, color = log(Population.density.per.square.miles))) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to Poverty %', 
    x = 'Percent.living.under.the.federal.poverty.line..2018.', 
    y = 'Case.Rate.per.100000',
    color = 'log(Population Density)'
  )
```
```{r}
df %>% 
  ggplot(aes(X65., Case.Rate.per.100000, color = log(Population.density.per.square.miles))) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to 65+ Percentage', 
    x = 'X65+.', 
    y = 'Case.Rate.per.100000',
    color = 'log(Population density)'
  )
```

```{r}
df %>% 
  ggplot(aes(Percent.Unemployed..2018., Case.Rate.per.100000, color = log(Population.density.per.square.miles))) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to Unemployed Percentage', 
    x = 'Percent.Unemployed..2018.', 
    y = 'Case.Rate.per.100000',
    color = 'log(Population density)'
  )
```

### Regression

According to the regression results, no coefficients regarding the demographic variables investigated in model 2 are statistically significant. There is no statistically meaningful relationship that could be concluded by now.

#### Model 1-a
$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 Population.Density.Per.Square.Miles
\end{aligned}
$$

```{r}
model1a <- lm(Case.Rate.per.100000 ~ Population.density.per.square.miles, data = df)
coeftest(model1a, vcov = vcovHC)
```
#### Model 1-b
$$
Case.Rate.Per.100000 =\beta_0 +\beta_1 log(Population.Density.Per.Square.Miles)
$$
```{r}
model1b <- lm(Case.Rate.per.100000 ~ log(Population.density.per.square.miles) , data = df)
coeftest(model1b, vcov = vcovHC)

```
#### Model 2-a
$$
\begin{aligned}
 Case.Rate.Per.100000 =\beta_0 &+\beta_1 log(Population.Density.Per.Square.Miles)\\&+\beta_2(White.Percentage.of.total. population)
\end{aligned}
$$

```{r}
model2a <- lm(Case.Rate.per.100000 ~ log(Population.density.per.square.miles)+ White...of.Total.Population, data = df)
coeftest(model2a, vcov = vcovHC)

$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 log(Population.Density.Per.Square.Miles)\\ &+ \beta_2(White.Percentage.of.total. population)^2
\end{aligned}
$$
```{r}
model2a <- lm(Case.Rate.per.100000 ~ log(Population.density.per.square.miles)+ I((White...of.Total.Population)^2), data = df)
coeftest(model2a, vcov = vcovHC)
```
$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 + \beta_2(White.Percentage.of.total. population)^2
\end{aligned}
$$
```{r}
model2a <- lm(Case.Rate.per.100000 ~ I((White...of.Total.Population)^2), data = df)
coeftest(model2a, vcov = vcovHC)

@@

#### Model 2-b
$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 log(Population.Density.Per.Square.Miles)\\ &+ \beta_2(White.Percentage.of.total. population)\\ &+\beta_3(Percen.living.under.the.federal.poverty.line.2018)
\end{aligned}
$$

```{r}
model2b <- lm(Case.Rate.per.100000 ~log(Population.density.per.square.miles)+ White...of.Total.Population+Percent.living.under.the.federal.poverty.line..2018., data = df)
coeftest(model2b, vcov = vcovHC)

@@

$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 log(Population.Density.Per.Square.Miles)\\ &+ \beta_2(White.Percentage.of.total. population)^2\\ &+\beta_3(Percen.living.under.the.federal.poverty.line.2018)
\end{aligned}
$$
```{r}
model2b <- lm(Case.Rate.per.100000 ~log(Population.density.per.square.miles)+ I((White...of.Total.Population)^2) + Percent.living.under.the.federal.poverty.line..2018., data = df)
coeftest(model2b, vcov = vcovHC)

```
$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_3(Percen.living.under.the.federal.poverty.line.2018)
\end{aligned}
$$
```{r}
model2b <- lm(Case.Rate.per.100000 ~ Percent.living.under.the.federal.poverty.line..2018., data = df)
coeftest(model2b, vcov = vcovHC)
```

#### Model 2-c

$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 log(Population.Density.Per.Square.Miles)\\ &+ \beta_2(White.Percentage.of.total. population)^2\\ &+\beta_4(Percent.Unemployed..2018.)
\end{aligned}
$$
```{r}
model2c <- lm(Case.Rate.per.100000 ~log(Population.density.per.square.miles)+ I((White...of.Total.Population)^2) + Percent.Unemployed..2018., data = df)
coeftest(model2c, vcov = vcovHC)

```
$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0+\beta_4(Percent.Unemployed..2018.)
\end{aligned}
$$
```{r}
model2c <- lm(Case.Rate.per.100000 ~ Percent.Unemployed..2018., data = df)
coeftest(model2c, vcov = vcovHC)

#### Model 2-d

$$
\begin{aligned}
Case.Rate.Per.100000=\beta_0 &+\beta_1log(Population.Density.Per.Square.Miles)\\&+\beta_2(White.Percentage.of.total.population)\\&+\beta_3(Percen.living.under.the.federal.poverty.line.2018)\\&+\beta_5(65+)
\end{aligned}
$$
```{r}
model2d <- lm(Case.Rate.per.100000 ~log(Population.density.per.square.miles)+ White...of.Total.Population+Percent.living.under.the.federal.poverty.line..2018.+X65., data = df)
coeftest(model2d, vcov = vcovHC)
```
## Model 2-d
$$
\begin{aligned}
Case.Rate.Per.100000=\beta_0 &+\beta_1log(Population.Density.Per.Square.Miles)\\&+\beta_2(White.Percentage.of.total.population)^2\\&+\beta_3(Percen.living.under.the.federal.poverty.line.2018)\\&+\beta_4(65+)
\end{aligned}
$$
```{r}
model2d <- lm(Case.Rate.per.100000 ~log(Population.density.per.square.miles)+ I((White...of.Total.Population)^2) + Percent.living.under.the.federal.poverty.line..2018.+X65., data = df)
coeftest(model2d, vcov = vcovHC)

$$
\begin{aligned}
Case.Rate.Per.100000=\beta_0+\beta_4(65+)
\end{aligned}
$$
```{r}
model2d <- lm(Case.Rate.per.100000 ~X65., data = df)
coeftest(model2d, vcov = vcovHC)

## Limitations of Model 2

The I.I.D assumption for CLM is not satisfied perfectly for all the models discussed above, since the states are not isolated from each other. It is impossible that states suffered from pandemic at different levels independently. Actually, the pandemic status across states tends to be highly related to each other.

In addition, all states are involved in the same market economy system even though there are economic performance divisions across the states. Moreover, in most states white race is still dominant in the population. Many states share the similar racial composition.
